### 2020-04-22 final_report/data.tex
Remove URLS and DOI from visible bibliography.

Kriging, or Gaussian process regression, is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}. Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.

>>>>

Kriging is a geostatistical surrogate modelling technique which relies on correlation functions over distance (lag) in the paramater space \cite{Bouhlel2018}. Although kriging performed poorly for our use case due to high dimensionality, these correlation measures gave insight into similarities between discrete-parameter slices of the data.

### 2020-04-22 final_report/methodology.tex
Remove URLS and DOI from visible bibliography.

Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain. We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space. MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution from the prior point. These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see \cite{Zhou2018} for a review).

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, Figure \label{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.

>>>>

Adaptive sampling techniques are widespread in the literature and have been specialised for surrogate modelling. Garud's \cite{Garud2016} "Smart Sampling Algorithm" achieved notable success by incorporating surrogate quality and crowding distance scoring to identify optimal new samples, but was only tested on a single-parameter domain. We theorised that a nondeterministic sample generation approach, built around Markov Chain Monte Carlo methods (MCMC), would fare better for high-dimensional models by more thoroughly exploring all local optima in the parameter space. MCMC produces a progressive chain of sample points, each drawn according to the same symmetric proposal distribution\footnote{An adaptive MCMC procedure \cite{Zhang2012}, which adjusts an ellipsoidal proposal distribution to fit the posterior, was also implemented but not fully tested.} from the prior point. These sample points will converge to a desired posterior distribution, so long as the acceptance probability for these draws has a particular functional dependence on that posterior value (see \cite{Zhou2018} for a review).

@@

We designed the Quality-Adaptive Surrogate Sampling algorithm (QASS, \cref{fig:qassplan}) to iteratively increment the training/test set with sample points which maximise surrogate error and minimise a crowding distance metric (CDM) \cite{Solonen2012} in parameter space. On each iteration following an initial training of the surrogate on $N$ uniformly random samples, the surrogate was trained and AE calculated. MCMC was then performed on the error function generated by performing nearest-neighbor interpolation on these test error points. The resultant samples were culled by $50\%$ according to the CDM, and then the $n$ highest-error candidates were selected for reintegration with the training/test set, beginning another training epoch. Validation was also performed during each iteration on independent, uniformly-random sample sets.

### 2020-04-22 final_report/results.tex
Remove URLS and DOI from visible bibliography.

\begin{wrapfigure}{r}{0.4\textwidth}
  \vspace{-60pt}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR model with two continuous parameters, wavenumber 1}
    \label{fig:sintoy}
  \end{center}
  \vspace{-30pt}
\end{wrapfigure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
    \caption{Absolute training error for QASS, uniform random scheme, and mixed scheme}
  \label{fig:qasssampling}
\end{figure}

Such tests revealed that while QASS has unmatched performance on its own adaptively-sampled training set, it is outperformed by the baseline scheme on uniformly random evaluation sets. We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices. Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, and is also shown in Figure \ref{fig:qasssampling}.

>>>>

\begin{wrapfigure}{r}{0.4\textwidth}
  \vspace{-60pt}
  \begin{center}
    \includegraphics[width=0.4\textwidth]{fig5_sintoy.jpg}
	\caption{Sinusoidal toy TBR theory over two continuous parameters, wavenumber 1}
    \label{fig:sintoy}
  \end{center}
  \vspace{-30pt}
\end{wrapfigure}

@@

\begin{figure}[h]
  \centering
    \includegraphics[width=0.8\linewidth]{fig7_qasssampling.pdf}
    \caption{Absolute training error for QASS, baseline scheme, and mixed scheme}
  \label{fig:qasssampling}
\end{figure}

Such tests revealed that while QASS has unmatched performance on its own adaptively-sampled training set, it is outperformed by the baseline scheme on uniformly random evaluation sets. We suspected that while QASS excels in learning the most strongly peaked regions of the TBR theory, this comes at the expense of precision in broader, smoother regions where uniformly random sampling suffices. Therefore a mixed scheme was implemented, with half MCMC samples and half uniformly random samples incremented on each iteration, which is also shown in Figure \ref{fig:qasssampling}.
